---
title: "EDA buscas"
output:
  html_document:
    df_print: paged
---

O objeto principal da análise são as buscas e a navegação depois da busca. Criamos esses dados a partir dos dados originais da wikimedia em `/data/search_data.csv`. 

Aqui, exploramos esses dados. 

```{r setup}
library(tidyverse)
library(here)
library(lubridate)
theme_set(theme_bw())
```

```{r ETL}
buscas = read_csv(here::here("data/search_data.csv"))
```

```{r}
buscas %>% 
    ggplot(aes(x = results)) + 
    geom_histogram(binwidth = 5) 
```

## 1.What is our daily overall clickthrough rate? How does it vary between the groups?

```{r}
buscas
```

## 2.Which results do people tend to try first? How does it change day-to-day?

## 3.What is our daily overall zero results rate? How does it vary between the groups?

```{r}
buscas %>%
    filter(results == 0)
```


## 4.Let session length be approximately the time between the first event and the last event in a session. Choose a variable from the dataset and describe its relationship to session length. 

uma sessão com 0 resultados dura pouco tempo 