---
title: "EDA buscas"
output:
  html_document:
    df_print: paged
---

## Lucas Raniére Juvino Santos

O objeto principal da análise são as buscas e a navegação depois da busca. Criamos esses dados a partir dos dados originais da wikimedia em `/data/search_data.csv`. 

```{r setup, echo=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(lubridate)
theme_set(theme_bw())
```

```{r echo=FALSE, warning=FALSE}
buscas = read_csv(here::here("data/search_data.csv"))
```

```{r echo=FALSE, warning=FALSE}
# processamento do dataset
# criação da variável dia, trocando os valores de first_click NA por 0, e exclusão dos outliers

buscas <- buscas %>%
            mutate(day = round_date(buscas$session_start_date, "day")) %>%
            filter(is.na(first_click) | first_click < 500)         

buscas_a <- buscas %>%
              filter(group == 'a')

buscas_b <- buscas %>%
              filter(group == 'b')
```

## 1.What is our daily overall clickthrough rate? How does it vary between the groups?

```{r echo=FALSE, warning=FALSE}
# clickthrough rate: the proportion of search sessions where the user clicked on one of the results displayed
buscas_a %>%
  group_by(session_id, group, day) %>%
  summarise(c_clicks = any(num_clicks > 0)) %>%
  ungroup() %>%
  group_by(day) %>%
  summarise(clickt_rate = sum(c_clicks) / n()) %>%
  ggplot(aes(x = day, y = clickt_rate)) +
  geom_point() +
  geom_line() +
  ggtitle("Group A") +
  labs(x = "Day",
       y = "Clickthrough rate")

buscas_b %>%
  group_by(session_id, group, day) %>%
  summarise(c_clicks = any(num_clicks > 0)) %>%
  ungroup() %>%
  group_by(day) %>%
  summarise(clickt_rate = sum(c_clicks) / n()) %>%
  ggplot(aes(x = day, y = clickt_rate)) +
  geom_point() +
  geom_line() +
  ggtitle("Group B") +
  labs(x = "Day",
       y = "Clickthrough rate")


```


## 2.Which results do people tend to try first? How does it change day-to-day?

```{r echo=FALSE, warning=FALSE}
# first_click

buscas_a %>%
  filter(!is.na(first_click)) %>%
  group_by(day) %>%
  ggplot(aes(x = day, y = first_click)) +
  geom_point() +
  ggtitle("Group A") +
  labs(x = "Day",
       y = "First click")
  
buscas_b %>%
  filter(!is.na(first_click)) %>%
  group_by(day) %>%
  ggplot(aes(x = day, y = first_click)) +
  geom_point() +
  ggtitle("Group B") +
  labs(x = "Day",
       y = "First click")
```

## 3.What is our daily overall zero results rate? How does it vary between the groups?

```{r echo=FALSE, warning=FALSE}
buscas %>%
  filter(!is.na(results)) %>%
  mutate(t_results = results > 0) %>%
  group_by(day, group) %>%
  summarise(rate = 1 - (sum(t_results) / n())) %>%
  group_by(group) %>%
  ggplot(aes(x = day, y = rate, color = group)) +
  geom_point() +
  geom_line() +
  #facet_wrap(~group) +
  labs(x = "Day",
       y = "Zero results rate")
```


## 4.Let session length be approximately the time between the first event and the last event in a session. Choose a variable from the dataset and describe its relationship to session length. 

```{r echo=FALSE, warning=FALSE}
buscas %>%
    filter(session_length < 4000) %>%
    ggplot(aes(x = num_clicks, y = session_length/60)) +
    geom_point(alpha = .5)
```





